% Load packages
\documentclass[11pt]{article}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
\usepackage{pbyp}

\setlength{\parindent}{0pt} % No indents

\begin{document}

\begin{center}
\Large\bfseries A \LaTeX{} template for writing beautiful point-by-point responses
\end{center}

We would like to thank the reviewers \rev{1}, \rev{2}, \rev{3}, and the \revAE for their thorough review of our manuscript. Please find our point-by-point response below.

% Question by AE
\begin{question}{\QuestionRevAE{Q1}}\label{AE:Q1}
This is a comment by the associate editor.
\end{question}

\begin{response}
This is our response to this comment.
\end{response}


% There may be some general comments by the reviewers
\begin{question}{\QuestionRevA{General}}\label{R1:general}
This is a general comment about your paper
\end{question}

\begin{response}
This is our response to this general comment.
\end{response}

% First question by reviewer 1
\begin{question}{\QuestionRevA{Q1}}\label{R1:Q1}
I have some question.
\end{question}

\begin{response}
Here is our response. Please also see our response to \cref{AE:Q1}.
\end{response}

% First question by reviewer 2
\begin{question}{\QuestionRevB{Q1}}\label{R2:Q1}
I also have some question.
\end{question}

\begin{response}
Here is our response. We also updated this in the manuscript (\addlines)
    \begin{revised}
    We greatly improved our manuscript by incorporating everything that the reviewer suggested! We even reference \cite{knuth1986} as they requested!
    \end{revised}
Thank you for the great comments!
\end{response}

% Second question by reviewer 2
\begin{question}{\QuestionRevB{Q2}}\label{R2:Q2}
I have another question
\end{question}
\begin{response}
Here is our response. Please also see our responses to \cref{AE:Q1,R1:Q1,R2:Q1}.
\end{response}


% References
\begin{thebibliography}{10}
\bibitem{knuth1986}
Donald E. Knuth (1986) \emph{The \TeX{} Book}, Addison-Wesley Professional.
\end{thebibliography}

\end{document}